cardinalR: Generating interesting high-dimensional data structures

### 2025-04-25 paper-cardinalR.Rmd
Added second application data

```{r projections}

@@

>>>>

```{r five-clusts-projections}

@@

```{r gen-three-clust-data}

positions <- geozoo::simplex(p=4)$points[1:3, ]
positions <- positions * 0.8

## To generate data
three_clusts <- gen_multicluster(n = c(750, 500, 250), p = 4, k = 3,
                       loc = positions,
                       scale = c(1, 1, 0.3),
                       shape = c("nonlinear", "pyrtri", "gaussian"),
                       rotation = NULL,
                       is_bkg = FALSE)

noise_df <- gen_noisedims(n = 1500, p = 3, m = rep(0, 3), s = rep(0.1, 3))
names(noise_df) <- paste0("x", 5:7)

three_clusts <- dplyr::bind_cols(three_clusts, noise_df)

three_clusts <- three_clusts |>
  dplyr::select(c(tidyselect::starts_with("x"), "cluster"))

three_clusts <- normalize_data(data = three_clusts)

```{r}
langevitour::langevitour(three_clusts[, -8])
```

```{r three-clusts-projections}
